### 2021-08-25 A methodological framework to enable the roaming agreement digitization: An NLP-based approach/paper.tex
25.08.21.7

\subsection{Designed Methodology}
Define abbreviations and acronyms the first time they are used in the text

\section{Implemented System}
Define abbreviations and acronyms the first time they are used in the text

>>>>

\subsection{Designed Methodology}
Define abbreviations and acronyms the first time they are used in the text.

\section{Implemented System}
The Fig.~\ref{fig1} shows a overall architecture of the NLP Engine that integrates over a docker infrastructure, establishing as inputs the Roaming Agreement text file, as well as the GSMA standard templates; as processing layer the logic associated to the NLP Engine and as output the classification of sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations} depending of the \textit{variables} detection.

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.25\textwidth]{images/NLP_Engine.png}}
\caption{NLP Engine overall architecture.}
\label{fig1}
\end{figure}

La primera consideración entorno a la arquitectura desarrollada radica en que el motor NLP se ha desarrollado como un Software Development Kit y por consiguiente este debe ser descagado y ejecutado desde un entrypoint.

En lo relativo a la implementación de la similaridad de Jaccard y a la similaridad del coseno.
